%%
%% This is file `skeleton.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% nuthesis.dtx  (with options: `skeleton')
%% 

%%
%% For common degrees, you can use the class options:
%% phd, edd, ms, ma
%% phd is the default
\documentclass[print,phd]{nuthesis}

\usepackage{caption}
\usepackage{framed}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{bibentry}
\usepackage{amsmath}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{wrapfig}
\usepackage{lscape}
\usepackage{rotating}
\usepackage{epstopdf}
\usepackage{color}
\usepackage{subfig}
\usepackage{afterpage}
\nobibliography*

\lstset{
	breaklines=true, 
	breakatwhitespace=true,
	frame=lines,
	basicstyle=\ttfamily,
	showstringspaces=false
}

\definecolor{grey}{rgb}{0.9,0.9,0.9}

\setcounter{tocdepth}{1}

\begin{document}
%% Start formatting the first few special pages
%% frontmatter is needed to set the page numbering correctly
\frontmatter

\title{Enabling Distributed Scientific Computing on the Campus}
\author{Derek Weitzel}
\adviser{Professor David Swanson}
\adviserAbstract{David Swanson}
\major{Computer Science}
\degreemonth{July}
\degreeyear{2015}
%%
%% For most people the defaults will be correct, so they are commented
%% out. To manually set these, just uncomment and make the needed
%% changes.
%% \college{Your college}
%% \city{Your City}
%%
%% For most people the following can be changed with a class
%% option. To manually set these, just uncomment the following and
%% make the needed changes.
%% \doctype{Thesis or Dissertation}
%% \degree{Your degree}
%% \degreeabbreviation{Your degree abbr.}
%%
%% Now that we know everything we need, we can generate the title page
%% itself.
%%
\maketitle
%%
%% You have a maximum of 350 words for your abstract, which includes
%% your title, name, etc.
%%
%% Required
\begin{abstract}
Campus research computing has evolved from many small decentralized resources, such as individual desktops, to fewer, larger centralized resources, such as clusters.  This change has been necessitated by the increasing size of researcher's workloads, but this change has harmed the researcher's user experience.  We propose to improve the user experience on the computational resources by creating an overlay cluster they are able to control.  This overlay should transparently scale to national cyberinfrastructure as the user's demands increase.

We explore methods for improving the user experience when submitting jobs on a campus grid.  To this end, we created a remote submission and overlay computational framework called Bosco.  This framework can remotely submit processing from the user's laptop to clusters on the campus or on national cyberinfrastructure.  To illustrate the possibilities of improving the user experience of remote submission, we created BoscoR, an interface to Bosco in the popular statistics and data processing programming language, R.  Bosco improves the user experience of submitting to campus clusters, while also being an efficient method for job management.

In order to solve some of the issues with data distribution on opportunistic resources, we created the CacheD, a data management framework for managing and provisioning storage resources on the campus.  The CacheD additionally optimizes transfers to multiple resources by using the peer-to-peer transfer protocol, BitTorrent.  Further, the CacheD optimizes shared data between multiple jobs by caching the input data directly on the execution resources.  The CacheD decreases the stage-in time over current transfer methods and significantly decreases stage-in time when the data is already cached.

Finally, we explain how to control data distribution on a campus through a comprehensive policy framework.  This framework is implemented in the CacheD.  We present the policy language, available attributes, and how to extend the policy language beyond the default behavior.  Multiple examples are given for different data distribution scenarios observed on campus resources.   

Combining easy-to-use campus job submission with Bosco, efficient data distribution with the CacheD, and a policy language to manage the data distribution, we have created a unified framework for campus computing.
	
	
	
%Campus research computing has evolved from many small decentralized resources, such as individual desktops, to fewer, larger centralized resources, such as clusters.  This change has been necessitated by the increasing size of researcher's workloads, but this change has harmed the researcher's user experience.  When the resources were decentralized, they may have been under the user's desk or just down the hall from their research lab.  They had privileges to install software that could control the scheduling of their computationally intensive jobs and manage their storage resources.  Now, as we have moved towards fewer but larger centralized computational resources, the users have fewer privileges than they enjoyed previously.  They cannot install software on the centralized campus clusters.  The scheduling of their jobs and the storage is managed centrally.
%
%We propose that users should have their privileges restored onto the computational resources by creating an overlay cluster they are able to control.  Both job submission and data distribution should come from the user's computer to the campus resources.  Additionally, these methods should transparently scale to national cyberinfrastructure as the user's demands increase.
%
%First, we explore methods for improving the user experience when submitting jobs on a campus grid.  To this end, we created a remote submission and overlay computational framework called Bosco.  This framework can remotely submit processing from the user's laptop to clusters on the campus or on national cyberinfrastructure.  To illustrate the possibilities of improving the user experience of remote submission, we created BoscoR, an interface to Bosco in the popular statistics and data processing programming language, R.  Bosco improves the user experience of submitting to campus clusters, while also being an efficient method for job management.
%
%Second, we discuss the issues with data distribution on the campus.  In order to solve some of the issues with data distribution on opportunistic resources, we created the CacheD, a data management framework for managing and provisioning storage resources on the campus.  The CacheD additionally optimizes transfers to multiple resources by using the peer-to-peer transfer protocol, BitTorrent.  Further, the CacheD optimizes shared data between multiple jobs by caching the input data directly on the execution resources.  The CacheD decreases the stage-in time over current transfer methods and significantly decreases stage-in time when the data is already cached.
%
%Third, we explain how to control data distribution on a campus through a comprehensive policy framework.  This framework is implemented in the CacheD.  We present the policy language, available attributes, and how to extend the policy language beyond the default behavior.  Multiple examples are given for different data distribution scenarios observed on campus resources.   
%
%Combining easy-to-use campus job submission with Bosco, efficient data distribution with the CacheD, and a policy language to manage the data distribution, we have created a unified framework for campus computing.


\end{abstract}

%% Optional
%% \begin{copyrightpage}
%% \end{copyrightpage}

%% Optional
%% \begin{dedication}
%% \end{dedication}

%% Optional
\begin{acknowledgments}
%TODO: Make an acknowledgments
I am thankful to have worked with many fine people throughout graduate school.

Dr. David Swanson, my dissertation advisor, has provided a fertile environment of both distributed computing users and the resources to test and provide solutions.  In addition, I am forever thankful for the opportunity he provided for me to attend graduate school.

Dr. Brian Bockelman has provided immense guidance for my dissertation.  I thank Brian for mentoring me throughout my collegiate career.

I thank my colleagues at the Holland Computing Center.  I have broken their systems, asked for advice, and caused an untold amount of extra work for them.  I could not have completed this dissertation without the skilled experts at HCC who have helped me throughout the process.

I would also like to thank my colleagues in the Open Science Grid.  They have provided me with a fellowship and internships in support of my Ph.D.  I would like to especially thank Ruth Pordes and Dan Fraser for providing valuable advice and mentorship in my academic career.

My family deserves thanks for many intangible gifts.  I thank them for encouraging me to complete my goals.

Last but not least, I thank my lovely fianc\'ee Katie for providing immeasurable support. 

\end{acknowledgments}

%% Optional
%% \begin{grantinfo}
%% \end{grantinfo}
%% The ToC is required
%% Uncomment these if need be

%% The ToC is required
\tableofcontents
%% Uncomment these if need be
\listoffigures
\listoftables
%%
%% ``Real'' beginning of the document.
%% mainmatter is needed to set the page numbering correctly
%%   mainmatter is needed after the ToC, (LoF, and LoT) to set the
%%   page numbering correctly for the main body
\mainmatter

%% Thesis goes here

\input{Introduction.tex}



\input{Background.tex}

\chapter{Campus Job Distribution}
\input{CampusJobs.tex}



\chapter{Campus Data Distribution}

\input{CampusDataDistribution.tex}

\chapter{Campus Storage Policy Language}
\input{CampusStoragePolicyLanguage.tex}

\chapter{Conclusion}
\input{Conclusion.tex}

%% backmatter is needed at the end of the main body of your thesis to
%% set up page numbering correctly for the remainder of the thesis
\backmatter

%% Start the correct formatting for the appendices
\appendix

%% Appendices go here (if you have them)

%% Bibliography goes here (You better have one)
%% BibTeX is your friend

\bibliographystyle{plain}
\bibliography{DerekWeitzelDissertation}

%% Index go here (if you have one)
\end{document}

\endinput
%%
%% End of file `skeleton.tex'.
